Reduced growth due to belowground sink limitation is not fully explained by reduced photosynthesis

### 2016-06-17 manuscript/manuscript_pve.Rmd
added cites and edits from BM

\
Alternatively, sink limitation can be investigated by manipulating plant tissue C sinks, for example by fruit remove or phloem girdling. In these studies, down regulation of *A*~n~ is often observed, and typically correlates with carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@urban2007girdling; @haouari2013fruit]. However, reductions in *A*~n~ have also been attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic] and stomatal limitation [@li2005photosynthesis]. This lack of continuity among findings is not surprising, as we still know little about the balance between assimilation, storage and growth across temporal scales in plants [@smith2007coordination]. As these manipulations likely impact source as well as sink activity simultaneously, affect water transport, are very extreme, or are specific to the occurrence of large fruiting sinks, they tell us little about source-sink coordination in typical growing conditions for woody species.

@@

*delete bellow*
This conclusion arises because plants grown in small containers are shown to accumulate leaf starch while having lower assimilation rates [@robbins1988effect]. However, evidence in support for a trade-off between C storage and growth in trees is, to date, inconclusive [@palacio2014does]. Whether down regulation of *A*~n~ and subsequent reductions of growth are quantitatively similar has rarely been tested. Based on these previous studies, using a range of container sizes as a sink-strength manipulation provides a way to empirically test the extent to which growth and *A*~n~ are coordinated.

@@

\
Forty-nine *Eucalyptus tereticornis* seedlings, 20 weeks old and approximately 40 cm tall in tube stock, were chosen from a single local Cumberland plain cohort. Six additional seedlings were harvested before planting to measure initial leaf area and dry mass of leaves, stems and roots. Previous container experiments have confirmed that species with tap roots (similar to *E. tereticornis*) use the center of the container as the medium for thick roots, leaving the periphery of the soil as the most active sites for fine root proliferation [@biran1980a; @biran1980b]. By using a species with tap root growth and manipulations of container length rather than width, we believed that a more realistic test of growth inhibition through constrained soil volume would be achieved.

@@

##Net carbon uptake model
The daily net C gain of seedlings (*G*), from @makela1997carbon, is given by

@@

##Whole-plant C balance
Optimization of the default model (*M*~free~) against data yielded an estimate of LMF of 25.7 %; with this LMF, the model predicted mean harvest total biomass of free seedlings within 1.0 %. Using this optimized LMF, the modeled total biomass of seedlings for each soil volume treatment (*M*~pots~) was on average 11&pm;2.3 g C more than measured seedling biomass when compared against predicted total net leaf C gain (Figure `r massmodelfig`a). As a result, seedling C mass was overestimated by an average of 45&pm;6.2 % in modeled seedlings across the soil volume treatments when non-photosynthetic parameters were kept constant (Figure `r massmodelfig`b). As a result, the observed reductions in leaf *A* with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the container size treatments.

#Discussion
This study utilized a novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling biomass production. Our goal was to identify how sink limitation of growth modified the carbon balance of seedlings. We found a strong reduction of growth in containerized plants. Leaf *A*~n~ was also strongly reduced, but this reduction was insufficient to fully explain the reduction in growth, implying that whole-plant respiratory loss was likely affected as well.

We addressed questions regarding the coordination of *A*~n~ and growth by complementing empirical results with a C mass balance model.

*Poorter review talks about water availability (rule out) temperature effects on soil volume (can rule out) nutrient availability (possible) root signaling (magic) but strangely, not carbohydrate feedback*

>>>>

\
Alternatively, sink limitation can be investigated by manipulating plant tissue C sinks, for example by fruit remove or phloem girdling. In these studies, down regulation of *A*~n~ is often observed, and typically correlates with carbohydrate accumulation resulting from reduced tissue sink strength  [@iglesias2002regulation;@urban2007girdling; @haouari2013fruit]. However, reductions in *A*~n~ have also been attributed to biochemical limitations prior to carbohydrate accumulation [@nebauer2011photosynthesis], irreversible photo-oxidative damage [@duan2008photosynthetic] and stomatal limitation [@li2005photosynthesis]. 
*In addition, it is unclear whether these impacts on An can fully explain the resulting impacts on growth, (? Has anyone attempted to determine this? Is there any evidence for impacts on respiration??)*

@@

@@

\
Forty-nine *Eucalyptus tereticornis* seedlings, 20 weeks old and approximately 40 cm tall in tube stock, were chosen from a single local Cumberland plain cohort. Six additional seedlings were harvested before planting to measure initial leaf area and dry mass of leaves, stems and roots. Previous container experiments have confirmed that species with tap roots (similar to *E. tereticornis*) use the center of the container as the medium for thick roots, leaving the periphery of the soil as the most active sites for fine root proliferation [@biran1980a; @biran1980b]. By using a species with taproot growth and manipulations of container length rather than width, we believed that a more realistic test of growth inhibition through constrained soil volume would be achieved.

@@

##Modelled net seedling C uptake
The daily net C gain of seedlings (*G*), from @makela1997carbon, is given by

@@

##Whole-plant C balance
*this needs to reflect C gain vs mass*
Optimization of the default model (*M*~free~) against data yielded an estimate of LMF of 25.7 %; with this LMF, the model predicted mean harvest total biomass of free seedlings within 1.0 %. Using this optimized LMF, the modeled total biomass of seedlings for each soil volume treatment (*M*~pots~) was on average 11&pm;2.3 g C more than measured seedling biomass when compared against predicted total net leaf C gain (Figure `r massmodelfig`a). As a result, seedling C mass was overestimated by an average of 45&pm;6.2 % in modeled seedlings across the soil volume treatments when non-photosynthetic parameters were kept constant (Figure `r massmodelfig`b). As a result, the observed reductions in leaf *A* with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the container size treatments.

#Discussion
This study utilized a novel field design to manipulate belowground sink limitation and physically restrict *Eucalyptus tereticornis* seedling biomass production. Our goal was to identify how sink limitation of growth modified the C balance of seedlings. We found a strong reduction of growth in containerized plants. Leaf *A*~n~ was also strongly reduced, but this reduction was insufficient to fully explain the reduction in growth, implying that components such as whole-plant respiratory loss were also likely affected.
